Faithful Variable Screening for High-Dimensional Convex Regression

### 2014-07-17 tex/scam/additive_faithful.tex
made a pass over sec 3.1

Lemma~\ref{lem:general_int_reduction} follows from the stationarity
conditions of the optimal solution.   This result is known, and
criterion \eqref{eq:backfit} is used in the backfitting
algorithm for fitting additive models.   We include 
a proof of the result as our results build on it.
% perhaps include this in an appendix??

@@

If $F$ is the uniform distribution,
then $f^*_k(x_k) = \displaystyle\int f(x_k, \mathbf{x}_{-k})
d\mathbf{x}_{-k}$.

\begin{example} Using Corollary~\ref{cor:product_int_reduction}, we
  give two examples of \emph{additively unfaithfulness} under the
  uniform distribution---where relevant variables are
  erroneously marked as irrelevant under an additive
  approximation. First, consider the following function:
\[
f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2)\quad
\trm{(egg carton)} 
\]
defined for $(x_1, x_2) \in [0,1]^2$.  Then
$\displaystyle\int_{x_2} f(x_1, x_2) d x_2 = 0$ and
$\displaystyle\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_1$ and $x_2$. An additive approximation
would set $f_1 = 0$ and $f_2 = 0$.  Next, consider the function
\[
f(x_1, x_2) = x_1 x_2 \quad \trm{(tilting slope)} 
\]
defined for $x_1 \in [-1,1],\; x_2 \in [0,1]$.  In this case
$\displaystyle\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_2$; therefore, we expect $f_2 = 0$ under the additive approximation. This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope $x_2$.
\end{example}

@@

Suppose we have the additive approximation
\begin{equation}
\label{eqn:unconstrained_additive}
f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
             \E \Bigl[\bigl( f(X) - \sum_{k=1}^s f_k(X_k) -\mu \bigr)^2 \Bigr]
         \,:\, \E f_k(X_k) = 0 \Bigr\}.
\end{equation}
We say that $f$ is \textit{additively faithful} under $F$ in case
$f^*_k = 0$ implies that $f$ does not depend on coordinate $k$.
\end{definition}

% We can define the support $\trm{supp}(f) \coloneqq \{ k \,:\,
% \trm{$k$ is relevant to $f$}\}$. Let $f^* = \sum_{k=1}^s$, then $f$
% is additively faith if $\trm{supp}(f) = \trm{supp}(f^*)$.

@@

Remarkably, under a general class of distributions which we characterize below, convex multivariate functions are additively faithful.

\begin{definition}
\label{defn:boundary-point}
Let $p(\mathbf{x})$ be a density supported on $[0,1]^s$, $p$ satisfies the \emph{boundary-points condition} if, for all $j$, and for all $\mathbf{x}_{-j}$:

\[
\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0
\quad \trm{at } x_k = 0, x_k = 1
\]

@@

The boundary-points condition is a weak condition. For instance, it is satisfied when the density is flat at the boundary of support, more precisely, when the \emph{joint density} satisfies the properties that $\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} =  \frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at points $x_j = 0, x_j=1$. The boundary-points property is also trivially satisfied when $p$ is the density of any product distributions.

@@

\begin{theorem}
\label{thm:convex_faithful}
Let $p$ be a positive density supported on $C=[0,1]^s$ that satisfies the boundary-points property (definition~\ref{defn:boundary-point}). If $f$ is convex and twice differentiable, then $f$ is \emph{additively faithful} under $p$.
\end{theorem}

@@

We pause to give some intuition before we present the full proof: 
suppose the underlying distribution is a product distribution for a second, 
then we know from lemma~\ref{lem:general_int_reduction} that the
additive approximation zeroes out $k$ when, fixing $x_k$, every
``slice'' of $f$ integrates to zero. We prove
Theorem~\ref{thm:convex_faithful} by showing that ``slices'' of convex
functions that integrate to zero cannot be ``glued'' together while
still maintaining convexity.

\begin{proof} (of Theorem~\ref{thm:convex_faithful})\\
Fix $k$. Using the result of Lemma~\ref{lem:general_int_reduction}, we need only show that for all $x_k$, $ \E[ f(X) - \sum_{k'} f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ implies that $f$ does not depend on coordinate $k$, i.e., $\partial_{x_k} f(\mathbf{x}) = 0$ for all $\mathbf{x}$.\\

Let us then use the shorthand notation that $r(\mathbf{x}_{-k}) = \sum_{k' \neq k} f_{k'}(x_{k'})$ and assume without loss of generality that $\mu = 0$. We then assume that for all $x_k$,

\[
 \E[ f(X) - r(X_{-k})  \given x_k] \equiv 
 \int_{\mathbf{x}_{-k}}  p(\mathbf{x}_{-k} \given x_k ) 
 \big(f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) = 0
\]

We let $p'(\mathbf{x}_{-k} \given x_k)$ denote 
$\frac{\partial p(\mathbf{x}_{-k} \given x_k)}{\partial x_k}$ and 
$p''(\mathbf{x}_{-k} \given x_k)$ denote 
$\frac{\partial^2 p(\mathbf{x}_{-k} \given x_k)}{\partial x_k^2}$ and likewise for $f'(x_k, \mathbf{x}_{-k})$ and $f''(x_k, \mathbf{x}_{-k})$. We then differentiate under the integral, which is valid because all functions are bounded.

\begin{align}
& \int_{\mathbf{x}_{-k}} p'(\mathbf{x}_{-k} \given x_k) 
\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) + 
p(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}  = 0 
\label{eqn:integral1a} \\
& \int_{\mathbf{x}_{-k}} p''(\mathbf{x}_{-k} \given x_k) 
\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big)  + 
2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) +
p(\mathbf{x}_{-k} \given x_k) f''(x_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  = 0 
\end{align}

By the boundary-points condition, we have that $p''(\mathbf{x}_{-k} \given x_k)$ and $p'(\mathbf{x}_{-k} \given x_k)$ are zero at $x_k = x_k^0 \equiv 0$. The integral equations reduce to the following then:
\begin{align}
& \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f'(x^0_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}= 0 \label{eqn:integral1b} \\
& \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f''(x^0_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k} = 0
\end{align}

Because $f$ is convex, $f(x_k, \mathbf{x}_{-k})$ must be a convex function of $x_k$ for all $\mathbf{x}_{-k}$. Therefore, for all $\mathbf{x}_{-k}$, $f''(x^0_k, \mathbf{x}_{-k}) \geq 0$. Since $p(\mathbf{x}_{-k} \given x^0_k) > 0$ by assumption that $p$ is a positive density, we have that $\forall \mathbf{x}_{-k}, f''(x^0_k, \mathbf{x}_{-k}) = 0$ necessarily.\\

The Hessian of $f$ at $(x^0_k, \mathbf{x}_{-k})$ then has a zero at the $k$-th main diagonal entry. A positive semidefinite matrix with a zero on the $k$-th main diagonal entry must have only zeros on the $k$-th row and column \footnote{ See proposition 7.1.10 of \citet{HJ90}}, which means that \emph{at all $\mathbf{x}_{-k}$, the gradient of $f'(x^0_k, \mathbf{x}_{-k})$ with respect to $\mathbf{x}_{-k}$ must be zero}.

Therefore, $f'(x_k^0, \mathbf{x}_{-k})$ must be constant for all $\mathbf{x}_{-k}$. By equation~\ref{eqn:integral1b}, we conclude then that $f'(x_k^0, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$. We can use the same reasoning for the case where $x_k = x_k^1$ and deduce that $f'(x^1_k, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$. \\

Because $f(x_k, \mathbf{x}_{-k})$ as a function of $x_k$ is convex, it must be that, for all $x_k \in (0,1)$ and for all $\mathbf{x}_{-k}$:
\[
0 = f'(x_k^0, \mathbf{x}_{-k}) \leq f'(x_k, \mathbf{x}_{-k}) \leq 
    f'(x_k^1, \mathbf{x}_{-k}) = 0
\]

$f$ thus does not depend on $x_k$.
% Now we apply the first-order condition of convex functions to any two points $(x_k, \mathbf{x}_{-k})$ and $(x'_k, \mathbf{x}_{-k})$ where $x_k, x'_k \in [0,1]$:

@@

Theorem~\ref{thm:convex_faithful} plays an important role in our
sparsistency analysis, where we show that the additive
approximation is variable selection consistent (or ``sparsistent''), even when the true function is not
additive.

@@

Then we have a closed form for the additive approximation, which we prove in [TODO:appendix reference].
\begin{itemize}
\item If $f$ does not depend on $x_j$, then $f^*_j(x_j) = 0$.
\item If $f$ depends on $x_j$, then
\[
f^*_j(x_j) = H_j^\tran \Sigma_j x_j^2 + c_j x_j
\]
where $H_j, \Sigma_j$ are the $j$-th row of $H_j, \Sigma_j$ respectively. 
\end{itemize}
Let $H = [1, 2; 2,5]$ and let $\Sigma = [1, -\alpha; -\alpha, 1]$. It is easy to check then that if $\alpha=0.5$, then $f^*_1 = 0$ and additive faithfulness is violated, and if $\alpha > 0.5$, then $f^*_1$ is a concave function.
\end{example}

@@

Since the true regression function $f$ is convex, it is natural to ask when it is sufficient to estimate an convex additive model:
\begin{equation}
\label{eqn:convex_additive}
\{ f^*_k \}_{k=1}^s = \arg\min \Big \{ 
    \E\big( f(X) - \sum_{k=1}^s f_k(X_k) \big)^2 \,:\, f_k \in \mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
\end{equation}
where $\mathcal{C}^1$ is the set of univariate convex functions.

@@

\begin{theorem}
\label{thm:acdc_faithful}
Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ and satisfies the boundary-points condition. Suppose that $f$ is convex and twice-differentiable.

@@

\begin{corollary} 
\label{cor:faithfulness_extension}
Suppose $p(x)$ is a positive density on $[0,1]^p$ and it satisfies the boundary-points condition.

@@

Now suppose $f^*_k = 0$ and $g^*_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
\[
\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
\]
Since optimal $c^* = \frac{\mathbb{E} [ h(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
we know $\mathbb{E} [ h(X) X_k^2 ] = 
\mathbb{E} \Big[ \mathbb{E}[ h(X) \,|\, X_k] X_k^2 \Big] = 0$.\\

Because $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $h^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
\[
\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) 
       - c (h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
\]
Again, $c^* = \frac{\mathbb{E}[g(X)\big( 
            h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)]}{\mathbb{E}
        \big( h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)^2} = 0$, so
\begin{align*}
\mathbb{E}[ h(X) \big( h^*_k(X_k) + \alpha X_k^2 \big) ] &= 
\mathbb{E}[ h(X) h^*_k(X_k) ] \\
& = \mathbb{E}\Big[ \mathbb{E}[h(X) | X_k]  h^*_k(X_k) \Big] \\
& = \mathbb{E} h^*_k(X_k)^2 = 0
\end{align*}
Therefore, $h^*_k(x_k) = 0$.

>>>>

Lemma~\ref{lem:general_int_reduction} follows from the stationarity
conditions of the optimal solution.   This result is known, and
criterion \eqref{eq:backfit} is used in the backfitting
algorithm for fitting additive models.   We include 
a proof as our results build on it.
% perhaps include this in an appendix??

@@

In particular, if $F$ is the uniform distribution,
then $f^*_k(x_k) = \displaystyle\int f(x_k, \mathbf{x}_{-k})
d\mathbf{x}_{-k}$.

\begin{example} Using Corollary~\ref{cor:product_int_reduction}, we
  give two examples of \emph{additively unfaithfulness} under the
  uniform distribution---where relevant variables are
  erroneously marked as irrelevant under an additive
  approximation. First, consider the following function:
\begin{equation}
f(x_1, x_2) = \sin( 2\pi x_1) \sin( 2 \pi x_2)\quad
\trm{(egg carton)} 
\end{equation}
defined for $(x_1, x_2) \in [0,1]^2$.  Then
$\displaystyle\int_{x_2} f(x_1, x_2) d x_2 = 0$ and
$\displaystyle\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_1$ and $x_2$. An additive approximation
would set $f_1 = 0$ and $f_2 = 0$.  Next, consider the function
\begin{equation}
f(x_1, x_2) = x_1 x_2 \quad \trm{(tilting slope)} 
\end{equation}
defined for $x_1 \in [-1,1],\; x_2 \in [0,1]$.  In this case
$\displaystyle\int_{x_1} f(x_1, x_2) d x_1 = 0$ for each $x_2$; therefore, we expect $f_2 = 0$ under the additive approximation. This function, for every fixed $x_2$, is a zero-intercept linear function of $x_1$ with slope $x_2$.
\end{example}

@@

Suppose we have the additive approximation
\begin{equation}
\label{eqn:unconstrained_additive}
f_k^*, \mu^* \coloneqq \argmin_{f_1,\ldots, f_s, \mu} \Bigl\{ 
             \E \Bigl[\Bigl( f(X) - \sum_{k=1}^p f_k(X_k) -\mu \Bigr)^2 \Bigr]
         \,:\, \E f_k(X_k) = 0 \Bigr\}.
\end{equation}
We say that $f$ is \textit{additively faithful} under $F$ in case
$f^*_k = 0$ implies that $f$ does not depend on coordinate $k$.
\end{definition}

% We can define the support $\trm{supp}(f) \coloneqq \{ k \,:\,
% \trm{$k$ is relevant to $f$}\}$. Let $f^* = \sum_{k=1}^p$, then $f$
% is additively faith if $\trm{supp}(f) = \trm{supp}(f^*)$.

@@

We now show that under a general class of distributions which we
characterize below, convex multivariate functions are additively
faithful.

\begin{definition}
\label{defn:boundary-point}
A density $p(\mathbf{x})$ be a density supported on $[0,1]^p$ satisfies
the \emph{boundary points condition} if, for all $j$, and for all $\mathbf{x}_{-j}$:

\begin{equation}
\frac{\partial p(\mathbf{x}_{-j} \given x_j)}{\partial x_j}  =  
\frac{\partial^2 p(\mathbf{x}_{-j} \given x_j)}{\partial x_j^2} = 0
\quad \trm{at } x_k = 0, x_k = 1
\end{equation}

@@

The boundary points condition is a weak condition. For instance, it is
satisfied when the density is flat at the boundary of support---more
precisely, when the joint density satisfies the property that
$\frac{\partial p(x_j,\mathbf{x}_{-j})}{\partial x_j} =
\frac{\partial^2 p(x_j, \mathbf{x}_{-j})}{\partial x_j^2} = 0$ at
points $x_j = 0, x_j=1$. The boundary points property is also
trivially satisfied when $p$ is a product density.

@@

\begin{theorem}
\label{thm:convex_faithful}
Let $p$ be a positive density supported on $C=[0,1]^p$ that satisfies
the boundary points property. 
If $f$ is convex and twice differentiable, then $f$ is additively faithful under $p$.
\end{theorem}

@@

We pause to give some intuition before we presenting the full proof.
Suppose that the the underlying distribution has a product density.
Then we know from Lemma~\ref{lem:general_int_reduction} that the
additive approximation zeroes out $k$ when, fixing $x_k$, every
``slice'' of $f$ integrates to zero. We prove
Theorem~\ref{thm:convex_faithful} by showing that ``slices'' of convex
functions that integrate to zero cannot be ``glued'' together while
still maintaining convexity.

Fixing $k$ and using the result of
Lemma~\ref{lem:general_int_reduction}, 
we need only show that for all $x_k$, $ \E[ f(X) - \sum_{k'}
f_{k'}(X_{k'}) \given x_k] - \E f(X) = 0 $ 
implies that $f$ does not depend on coordinate $k$, i.e., 
$\partial_{x_k} f(\mathbf{x}) = 0$ for all $\mathbf{x}$.

Let us use the shorthand notation that $r(\mathbf{x}_{-k}) = \sum_{k'
  \neq k} f_{k'}(x_{k'})$ and assume without loss of generality that
$\mu = 0$. We then assume that for all $x_k$,
\begin{equation}
 \E[ f(X) - r(X_{-k})  \given x_k] \equiv 
 \int_{\mathbf{x}_{-k}}  p(\mathbf{x}_{-k} \given x_k ) 
 \big(f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) = 0.
\end{equation}
We let $p'(\mathbf{x}_{-k} \given x_k)$ denote 
$\frac{\partial p(\mathbf{x}_{-k} \given x_k)}{\partial x_k}$ and 
$p''(\mathbf{x}_{-k} \given x_k)$ denote 
$\frac{\partial^2 p(\mathbf{x}_{-k} \given x_k)}{\partial x_k^2}$ and
likewise for $f'(x_k, \mathbf{x}_{-k})$ and $f''(x_k,
\mathbf{x}_{-k})$. We then differentiate under the integral, valid
because all functions are bounded, and obtain
\begin{gather}
\int_{\mathbf{x}_{-k}} p'(\mathbf{x}_{-k} \given x_k) 
\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big) + 
p(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}  = 0 
\label{eqn:integral1a} \\
\int_{\mathbf{x}_{-k}} p''(\mathbf{x}_{-k} \given x_k) 
\big( f(\mathbf{x}) - r(\mathbf{x}_{-k}) \big)  + 2 p'(\mathbf{x}_{-k} \given x_k) f'(x_k, \mathbf{x}_{-k}) +
p(\mathbf{x}_{-k} \given x_k) f''(x_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k}  = 0 .
\end{gather}

By the boundary points condition, we have that $p''(\mathbf{x}_{-k}
\given x_k)$ and $p'(\mathbf{x}_{-k} \given x_k)$ are zero at $x_k =
x_k^0 \equiv 0$. The integral equations then reduce to the following:
\begin{align}
& \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f'(x^0_k, \mathbf{x}_{-k}) d \mathbf{x}_{-k}= 0 \label{eqn:integral1b} \\
& \int_{\mathbf{x}_{-k}} p(\mathbf{x}_{-k} \given x^0_k) f''(x^0_k, \mathbf{x}_{-k}) d\mathbf{x}_{-k} = 0.
\end{align}
Because $f$ is convex, $f(x_k, \mathbf{x}_{-k})$ must be a convex
function of 
$x_k$ for all $\mathbf{x}_{-k}$. Therefore, for all $\mathbf{x}_{-k}$,
$f''(x^0_k, \mathbf{x}_{-k}) \geq 0$. Since $p(\mathbf{x}_{-k} \given
x^0_k) > 0$ by the assumption that $p$ is a positive density, 
we have that $\forall \mathbf{x}_{-k}, f''(x^0_k, \mathbf{x}_{-k}) = 0$ necessarily.

The Hessian of $f$ at $(x^0_k, \mathbf{x}_{-k})$ then has a zero at
the $k$-th main diagonal entry. A positive semidefinite matrix with a
zero on the $k$-th main diagonal entry must have only zeros on the
$k$-th row and column; see proposition 7.1.10 of
\citet{HJ90}.  Thus, at all $\mathbf{x}_{-k}$, the
gradient of $f'(x^0_k, \mathbf{x}_{-k})$ with respect to
$\mathbf{x}_{-k}$ must be zero.
Therefore, $f'(x_k^0, \mathbf{x}_{-k})$ must be constant for all
$\mathbf{x}_{-k}$. By equation~\ref{eqn:integral1b}, we conclude 
that $f'(x_k^0, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$. We
can use the same reasoning for the case where $x_k = x_k^1$ and deduce
that $f'(x^1_k, \mathbf{x}_{-k}) = 0$ for all $\mathbf{x}_{-k}$.

Because $f(x_k, \mathbf{x}_{-k})$ as a function of $x_k$ is convex, it must be that, for all $x_k \in (0,1)$ and for all $\mathbf{x}_{-k}$,
\begin{equation}
0 = f'(x_k^0, \mathbf{x}_{-k}) \leq f'(x_k, \mathbf{x}_{-k}) \leq 
    f'(x_k^1, \mathbf{x}_{-k}) = 0
\end{equation}
Therefore $f$ does not depend on $x_k$.
% Now we apply the first-order condition of convex functions to any two points $(x_k, \mathbf{x}_{-k})$ and $(x'_k, \mathbf{x}_{-k})$ where $x_k, x'_k \in [0,1]$:

@@

Theorem~\ref{thm:convex_faithful} plays an important role in our
finite sample analysis, where we show that the additive
approximation is variable selection consistent (or ``sparsistent''), even when the true function is not
additive.

@@

Then we have a closed form for the additive approximation, which we prove in [TODO:appendix reference].
\begin{itemize}
\item If $f$ does not depend on $x_j$, then $f^*_j(x_j) = 0$.
\item If $f$ depends on $x_j$, then
\begin{equation}
f^*_j(x_j) = H_j^\tran \Sigma_j x_j^2 + c_j x_j
\end{equation}
where $H_j, \Sigma_j$ are the $j$-th row of $H_j, \Sigma_j$ respectively. 
\end{itemize}
Let $H = [1, 2; 2,5]$ and let $\Sigma = [1, -\alpha; -\alpha, 1]$. It is easy to check then that if $\alpha=0.5$, then $f^*_1 = 0$ and additive faithfulness is violated, and if $\alpha > 0.5$, then $f^*_1$ is a concave function.
\end{example}

@@

Since the true regression function $f$ is convex, it is natural to ask when it is sufficient to estimate an convex additive model:
\begin{equation}
\label{eqn:convex_additive}
\{ f^*_k \}_{k=1}^p = \arg\min \Big \{ 
    \E\big( f(X) - \sum_{k=1}^p f_k(X_k) \big)^2 \,:\, f_k \in \mathcal{C}^1, \, \E f_k(X_k) = 0 \Big \}
\end{equation}
where $\mathcal{C}^1$ is the set of univariate convex functions.

@@

\begin{theorem}
\label{thm:acdc_faithful}
Suppose $p(\mathbf{x})$ is a positive density on $C=[0,1]^p$ and satisfies the boundary points condition. Suppose that $f$ is convex and twice-differentiable.

@@

\begin{corollary} 
\label{cor:faithfulness_extension}
Suppose $p(x)$ is a positive density on $[0,1]^p$ and it satisfies the boundary points condition.

@@

Now suppose $f^*_k = 0$ and $g^*_k = 0$. Let $\sigma_k^2$ denote $\E X_k^2$. Then 
\begin{equation}
\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) - c (X_k^2-\sigma_k^2) \Big)^2 = 0
\end{equation}
Since optimal $c^* = \frac{\mathbb{E} [ h(X) (X_k^2-\sigma_k^2) ]}{\mathbb{E}[ X_k^2 ]}$, 
we know $\mathbb{E} [ h(X) X_k^2 ] = 
\mathbb{E} \Big[ \mathbb{E}[ h(X) \,|\, X_k] X_k^2 \Big] = 0$.\\

Because $\partial^2_{x_k} h^*_k(x_k)$ is lower bounded, for large enough $\alpha$, $h^*_k(x_k) + \alpha (x_k^2 - \sigma_k^2)$ has a non-negative second derivative and thus is convex. Then
\begin{equation}
\arg\min_{c \in \mathbb{R}} \mathbb{E}\Big( h(X) 
       - c (h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2)) \Big)^2 = 0
\end{equation}
Again, $c^* = \frac{\mathbb{E}[g(X)\big( 
            h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)]}{\mathbb{E}
        \big( h^*_k(X_k) + \alpha (X_k^2 - \sigma_k^2) \big)^2} = 0$, so
\begin{align*}
\mathbb{E}[ h(X) \big( h^*_k(X_k) + \alpha X_k^2 \big) ] &= 
\mathbb{E}[ h(X) h^*_k(X_k) ] \\
& = \mathbb{E}\Big[ \mathbb{E}[h(X) | X_k]  h^*_k(X_k) \Big] \\
& = \mathbb{E} h^*_k(X_k)^2 = 0
\end{align*}
Therefore, $h^*_k(x_k) = 0$.
